\Huge Stellar continuum modelling

### 2023-12-07 paper/main.tex
some stuff

@@

%Code is available at \url{https://github.com/andycasey/continuum} and is registered in the Python Package Index as \texttt{stellar-continuum}.

>>>>

\begin{figure}
    \caption{Median observed rectified flux values as a function of S/N ratio showing that there is no bias as a function of S/N ratio.}
\end{figure}

\begin{figure}
    \caption{Median model continuum-rectified flux values as a function of effective temperature, compared to the median observed rectified flux values as a function of Gaia colours, showing there is no bias as a function of spectral type?}
\end{figure}

\begin{figure}
    \caption{Gaia H-R diagram with each bin coloured by the median $\vecpsi_i$ value, picking some $i$th eigenspectra that looks like metallicity. \label{fig:gaia_hrd_metallicity}}
\end{figure}

@@

We solved continuum normalization.

Code is available at \url{https://github.com/andycasey/continuum} and is registered in the Python Package Index as \texttt{stellar-continuum}.
